Tables/Graphs for Article

### 2018-01-04 article/draft1.Rnw
edited intro + related works sections

Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge. Thousands of questions and answers are posted everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction and increase web traffic. This paper presents a survival analysis of the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.55, 95\% CI = (2.32, 2.80))), factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.88, 95\% CI = (8.20, 9.34))). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

As not all possible repairs are covered in the published guides and users may have additional questions related to existing guides, iFixit's \textit{Answers} forum is an important resource for users. This platform features questions pertaining to over 9,000 devices, ranging from jammed zippers to shattered iPhone screens and faulty vehicle air conditioners, with over 100,000 solutions. As thousands of users rely on this forum for information, it is important that users receive timely answers. Fast response times enhance user experience and increase web traffic, which is valuable to the reputation and longevity of the \textit{Answers} forum. Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times, and for how the forum design can be improved.

@@

With the recent increase in the popularity and use of CQAs, these platforms have been the subject of a multitude of studies related to information sciences. Regarding analysis of response times, \cite{Bhat2014} developed a classification model to estimate response times for questions posted on \textit{Stack Overflow}, using both tag-based and textual features. Analysis determine that tag-based features, like the number of ``popular'' tags a question contains or the number of users subscribed to a tag, were the best predictors of response time. \cite{Mahmud2013} proposed models based on exponential distributions to predict response times, and were built from users' previous wait times for responses.  Both \cite{Bhat2014} and \cite{Mahmud2013} restrict analysis to questions for which the response time is observed, ignoring unanswered questions; meanwhile \cite{Asaduzzaman2013} focused exclusively on characteristics of unanswered questions. \cite{Asaduzzaman2013} developed a taxonomy for classifying unanswered questions on \textit{Stack Overflow}, and developed a model to predict how long a question would remain unanswered using textual features like title and post length, and user features like the number of questions asked and answered by the user prior to posting. The research presented in this paper uses the framework of survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

The majority of existing research has been focused on predicting question and answer quality by using both textual and non-textual features of posts. \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com}, using primarily textual features (surface, lexical, syntactic, forum-specific, and similarity (relatedness of a post to the topic of the forum) features). \cite{Blumenstock} also determined that textual features, i.e word count, was the most accurate metric of Wikipedia article quality. Wikipedia articles can represent the same kind of user-generated content featured on CQAs. On the other hand, \cite{H.fu} found that non-textual features, like revision and comment count on an answer or the number of points or merit badges a user has, were the most useful indicators of answer quality across four different knowledge domains on \textit{Stack Exchange}. A number of other studies have also developed classification algorithms using both textual and non-textual features with the similar goal of predicting question and answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a}. \cite{Ravi2014} presented a slightly different approach by analyzing the content of posts and utilizing latent topic models to predict quality. \cite{Anderson2012} developed models to the predict the long term value of a question and its answers on \textit{Stack Overflow}. The present analysis combines both textual and non-textual features of questions on iFixit's \textit{Answers} forum in a Cox regression model to predict survival probability of questions.

>>>>

Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge. Thousands of questions and answers are posted by users everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction and increase web traffic. This paper presents a survival analysis of the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.55, 95\% CI = (2.32, 2.80))), factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.88, 95\% CI = (8.20, 9.34))). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

As not all possible repairs are covered in the published guides and users may have additional questions related to existing guides, iFixit's \textit{Answers} forum is an important resource for users. This platform features questions pertaining to over 9,000 devices, ranging from jammed zippers to shattered phone screens and faulty air conditioners, with over 100,000 solutions. As thousands of users rely on this forum for information, it is important that users receive timely answers. Fast response times enhance user experience and thus increase web traffic, which is valuable to the reputation and longevity of iFixit's \textit{Answers} forum. Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how the forum design can be improved.

@@

With the recent increase in the popularity and use of CQAs, these platforms have been the subject of a multitude of studies. Regarding analysis of response times, \cite{Bhat2014} developed a classification model to estimate response times for questions posted on \textit{Stack Overflow} using features of the questions. Analysis determined that tag-based features, like the number of ``popular'' tags a question contains or the number of users subscribed to a tag, were the best predictors. \cite{Mahmud2013} approached response time analysis with a different method, and proposed models to predict response times of questions posted on Twitter based on exponential distributions and built from users' previous wait times for responses. In contrast, \cite{Asaduzzaman2013} focused exclusively on unanswered questions and developed a taxonomy for classifying such questions on \textit{Stack Overflow}, and created a model to predict how long a question would remain unanswered using both textual features of the questions and characteristics of the user. All research mentioned restricted analysis to either questions for which response times were observed, or to questions that remained unanswered. The research presented in this paper uses the framework of survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

The majority of existing research has been focused on predicting question and answer quality by using both textual and non-textual features of posts. \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com}, using primarily textual features of the questions. \cite{Blumenstock} also determined that textual features, i.e word count, was the most accurate metric of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs). On the other hand, \cite{H.fu} found that non-textual features, like revision and comment count on an answer or the number of points or merit badges a user has, were the most useful indicators of answer quality across four different knowledge domains on \textit{Stack Exchange}. A number of other studies have also developed classification algorithms using both textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a} \cite{Ravi2014}. All research previously mentioned restricted analysis to predicting either question quality or answer quality. \cite{Anderson2012} presented models to predict the long term value or quality of questions as well as its answers on \textit{Stack Overflow}. The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors indicating high quality questions also lead to faster response times. (fix this section)

### 2018-01-04 article/draft1.tex
edited intro + related works sections

Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge. Thousands of questions and answers are posted everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction and increase web traffic. This paper presents a survival analysis of the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.55, 95\% CI = (2.32, 2.80))), factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.88, 95\% CI = (8.20, 9.34))). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

>>>>

Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge. Thousands of questions and answers are posted by users everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction and increase web traffic. This paper presents a survival analysis of the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.55, 95\% CI = (2.32, 2.80))), factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.88, 95\% CI = (8.20, 9.34))). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.
